### 2019-01-13 Publication/COLI-manual3.tex
refactor

\documentclass{clv3}

\usepackage{hyperref}
\usepackage{xcolor}
\definecolor{darkblue}{rgb}{0, 0, 0.5}
\hypersetup{colorlinks=true,citecolor=darkblue, linkcolor=darkblue, urlcolor=darkblue}

\bibliographystyle{compling}

% test compatibility with algorithmic.sty
%\usepackage{algorithmic}

\issue{1}{1}{2016}

%Document Head
\dochead{CLV3 Class File Manual}

\runningtitle{How to Use CLV3 \LaTeX\ Class File}

\runningauthor{Odi\'e N. Gementera}

\begin{document}

\title{How to Use CLV3 \LaTeX\ Class File}

\author{Odi\'e N. Gementera\thanks{PITC Building, Pascor Drive, Sto. Ni\~no, Para\~naque City, 1700 Philippines. E-mail: o.gementera@spi-bpo.com.}}
\affil{Publishing / SPi}

\author{Another Author\thanks{PITC Building}}
\affil{Publishing / SPi}

\author{And Another Author}
\affil{Publishing / SPi}

\author{And Yet Another}
\affil{Publishing / SPi}

\maketitle

\begin{abstract}
This article describes how to use the ``CLV3'' class file, developed by {\sf SPi}, 
to produce typeset papers based on Computer Linguistics typesetting specifications 
for submission to MIT. This document was produced using ``{\tt clv3}'' class file 
and will be modified whenever there is an update in the layout specifications.
\end{abstract}

\section{Introduction}

This document applies to version 3 of CL class file. Prior style files such as 
``{\tt cl.sty}'' and ``{\tt coli.sty}'' do not have all of the features 
described here. It is assumed that the user has a basic knowledge of \LaTeX\ 
typesetting commands.

\section{Class File Options}

There are several options that can be used to switch the mode of MIT2 from normal 
article to manuscript style, or to different layout styles. This is specified in 
the usual \LaTeX\ way by declaring:

\verb|\documentclass[bookreview,manuscript]{clv3}|

%\subsection{Default Option}

\begin{deflist}
\item[bookreview] Sets the article layout for Book Review.
\item[brief] Sets the article layout for Briefly Noted.
\item[discussion] Sets the article layout for Squibs and Discussions.
\item[pubrec] Sets the article layout for Publication Received.
\item[shortpaper] Sets the article layout for Short Paper.
\item[manuscript] Sets the baseline spacing to double space. This 
option can be used in combination with other options.
\end{deflist}

By not declaring any option in the \verb|\documentclass| command the class file
will automatically set to standard article layout.

\section{Title Page}

The title page is created using the standard \LaTeX\ command \verb|\maketitle|. 
Before this command is declared, the author must declare all the data which are 
to appear in the title area.\footnote{$\backslash$maketitle is the command to execute all the title page information.}

\subsection{Volume, Number and Year}

The command \verb|\issue{vv}{nn}{yyyy}| is used in declaring the volume, number
and year of the article. The first argument is for the volume, the second argument 
is for the issue number. Volume and Issue number will appear on the even page 
running head opposite the journal name. The third argument is for the Year which 
will appear in the copyright line at the bottom of the title page.

\subsection{Document Head}

Document head is produced with the command \verb|\dochead{Document Head}|. Doc head 
will output differently, or may not appear at all, depending on the option used in the 
documentclass.

\subsection{Paper Title}

The paper title is declared like: \verb|\title{Computer Linguistic Article}|
in the usual \LaTeX manner. Line breaks may be inserted with (\verb|\\|) to equalize 
the length of the title lines.

\subsection{Authors}
The name and related information for authors is declared with the \verb|\author{}| command.

The \verb|\thanks{}| command produces the ``first footnotes.''. \LaTeX\ \verb|\thanks| 
cannot accommodate multiple paragraphs, author will have to use a separate \verb|\thanks|
for each paragraph.

The \verb|\affil{}| command produces the author affiliations that appears right under 
the author's name.

\subsection{Running Headers}
The running heads are declared with the \verb|\runningtitle{Running Title}| for the 
journal name and \verb|\runningauthor{Author's Surname}| for author. These information 
will appear on the odd pages. For {\tt bookreview} option, odd page running head is 
automatically set to "Book Reviews". Even page running head is default to Computational 
Linguistics opposite volume and issue number.

\subsection{History Dates}

History dates are declared with \verb|\historydates{Submission received:...}|. This data
should contain Submission, Revised and Accepted date of the article. History dates appear
at the footnote area of title age.

\section{Abstract}

Abstract is the first part of a paper after \verb|\maketitle|. Abstract text is 
placed within the abstract environment:

\begin{verbatim}
\begin{abstract}
This is the abstract text . . .
\end{abstract}
\end{verbatim}

\section{Section Headings}

Section headings are declared in the usual \LaTeX\ way via \verb|\section{}|, 
\verb|\subsection{}|, \verb|\subsubsection{}|, and \verb|\paragraph{}|. The 
first 3 levels of section head will have Arabic numbering separated 
by period. The \verb|\paragraph{}| section will have the title head in Italics 
and at the same line with the first line of succeeding paragraph.

\section{Citations}
Citations in parentheses are declared using the \verb|\cite{}|
command, and appear in the text as follows: 
This technique is widely used \cite{woods}.
The command \verb|\citep{}| (cite parenthetical) is a synonym of \verb|\cite{}|.

Citations used in the sentence are declared using the \verb|\namecite{}|
commands, and appear in the text as follows: 
\namecite{woods} first described this technique.
The command \verb|\citet{}| (cite textual) is a synonym of \verb|\namecite{}|.

This style file is designed to be used with the BibTeX
style file \verb|compling.bst|.  Include the command
\verb|\bibliographystyle{compling}| in your source file.

Citation commands are based on the \verb|natbib| package;
for details on options and further variants of the commands,
see the \verb|natbib| documentation.  In particular, options 
exist to add extra text and page numbers.  For example, 
\verb|\cite[cf.][ch.\ 1]{winograd}| yields: \cite[cf.][ch.\ 1]{winograd}.

The following examples illustrate how citations appear both in the text
and in the references section at the end of this document.
\begin{enumerate}
\item Article in journal: 
 \namecite{akmajian};
 \namecite{woods}.
\item Book: 
  \namecite{altenberg};
  \namecite{winograd}.
\item Article in edited collection/Chapter in book: 
  \namecite{cutler};
  \namecite{sgall};
  \namecite{jurafsky}.
\item Technical report:
  \namecite{appelt};
  \namecite{robinson}.
\item Thesis or dissertation: 
  \namecite{baart};
  \namecite{spaerckjones};
  \namecite{cahn}.
\item Unpublished item: 
  \namecite{ayers}.
\item Conference proceedings: 
  \namecite{benoit}.
\item Paper published in conference proceedings: 
  \namecite{krahmer};
  \namecite{Copestake2001}.
\end{enumerate}

\section{Definition with Head}

Definition with head is declared by using the environment:
\\
\begin{verbatim}
\begin{definition}
Definition text. . .
\end{definition}
\end{verbatim}

This environment will generate the word {\bf ``Definition 1''} in bold on separate
line. The sequence number is generated for every definition environment. Definition 
data will have no indention on the first line while succeeding lines will have hang 
indention.

\section{Lists}

The usual \LaTeX\ itemize, enumerate and definition list environments are used 
in CLV3 style.

To produce Numbered List use the environment:

\begin{verbatim}
\begin{enumerate}
\item First numbered list item
\item Second numbered list item
\item Third numbered list item
\end{enumerate}
\end{verbatim}

To produce Bulleted List use the environment:

\begin{verbatim}
\begin{itemize}
\item First bulleted list item
\item Second bulleted list item
\item Third bulleted list item
\end{itemize}
\end{verbatim}

To produce Definition List use the environment:

\begin{verbatim}
\begin{deflist}
\item[First]  Definition list item. . .
\item[Second] Definition list item. . .
\item[Third]  Definition list item. . .
\end{deflist}
\end{verbatim}

Additional list environment were also defined such as Unnumbered, Arabic and Alpha lists.

Unnumbered List is the list where item labels are not generated. To produce Unnumbered List use the environment:

\begin{verbatim}
\begin{unenumerate}
\item First list item
\item Second list item
\item Third list item
\end{unenumerate}
\end{verbatim}

To produce Arabic List use the environment:

\begin{verbatim}
\begin{arabiclist}
\item First arabic list item
\item Second arabic list item
\item Third arabic list item
\end{arabiclist}
\end{verbatim}

To produce Alpha List use the environment:

\begin{verbatim}
\begin{alphalist}
\item First alpha list item
\item Second alpha list item
\item Third alpha list item
\end{alphalist}
\end{verbatim}

All the list environments mentioned above can be nested with each other.

\subsection{Other List Types}

\subsubsection{Outline List or Example List}

\begin{verbatim}
\begin{exlist}
\item First outline list item. . .
\item Second outline list item. . .
\item Third outline list item. . .
\end{exlist}
\end{verbatim}

\subsubsection{Output Formula or Algorithm}

\begin{verbatim}
\begin{algorithm}
\item[Step 1] First item. . . 
\item[Step 2] Second item. . .
\end{algorithm}
\end{verbatim}

% test compatibility with algorithmic.sty
%\begin{algorithmic}
%\STATE i
%\end{algorithmic}

See sample on the {\tt COLI-template.pdf}.

\section{Word Formula or Displayed Text}

Word formula and displayed text are text that should be displayed in a 
separate line without indention. This are achieved by using the environment:

\begin{verbatim}
\begin{displaytext}
This is a sample of displayed text . . .
\end{displaytext}
\end{verbatim}

\section{Dialogue}

Dialogue text are presentation of people's conversation. These will be presented 
on a separate line where each dialogue starts with the name of speaker, followed by 
colon. Succeeding lines will be hang indented. To produce Dialogue use the environment:
\\
\begin{verbatim}
\begin{dialogue}
Speaker 1: dialogue. . .

Speaker 2: dialogue. . .
\end{dialogue}
\end{verbatim}

\noindent Please make sure to insert an empty line between dialogues.

\section{Extracts}

Extract text acts like quote, where left and right margins are indented.
To produce Extract use the environment:

\begin{verbatim}
\begin{extract}
This is an example of Extract text. . .
\end{extract}
\end{verbatim}

\noindent See sample on the {\tt COLI-template.pdf}.

\section{Theorem-like Environments}

There are several theorem-like environments defined in CLV3 class file. Theorem-like
environments generate the name of the theorem as label, and counter number in bold.

\subsection{Example}

To produce Example use the environment:

\begin{verbatim}
\begin{example}
This is Example text. . .
\end{example}
\end{verbatim}

\subsection{Lemma}

To produce Lemma use the environment:

\begin{verbatim}
\begin{lemma}
Lemma text. . .
\end{lemma}
\end{verbatim}

This produces the following output:
\begin{lemma}\label{lem}
Lemma text.
\end{lemma}
A small vertical space separates the end of the lemma
from the following text.

\subsection{Theorem}

To produce Theorem use the environment:

\begin{verbatim}
\begin{theorem}
Theorem text. . .
\end{theorem}
\end{verbatim}

This produces the following output:
\begin{theorem}\label{thm}
Theorem text.
\end{theorem}
\noindent
A small vertical space separates the end of the theorem
from the following text.

\subsection{Proof}

The proof environment produces a square at the end of the text. To produce Proof 
use the environment:

\begin{verbatim}
\begin{proof}
Proof text. . .
\end{proof}
\end{verbatim}

This produces the following output:
\begin{proof}\label{proof}
Proof text.
\end{proof}
A small vertical space separates the end of the lemma
from the following text.

\subsection{Unnumbered Theorem-like Environments}

There are also unnumbered version of some of the theorem-like environments. 
These are declared by using its asterisked version. Here are the three 
unnumbered version of theorem-like environments:

\begin{verbatim}
\begin{theorem*}
Unnumbered theorem text. . .
\end{theorem*}
\end{verbatim}

\section{Appendix}

Appendix is declared by issuing the command \verb|\appendix|. This will set 
the necessary labels to appendix's rule (i.e. (A.1) for equation number).

Sections inside Appendix are declared using \verb|\appendixsection{}|, which 
will produce {\bf Appendix A: Section Title} for first section.

Equation numbers are automatically set to (A.1), (A.2) and (A.3). Where the letters 
follow the current level of Appendix section. So equations on {\bf Appendix B} 
will have equation numbers as follow: (B.1), (B.2) and (B.3).

\section{Acknowledgments}

Acknowledgments are produce by using the environment:
\\
\begin{verbatim}
\begin{acknowledgments}
Acknowledgments text. . .
\end{acknowledgments}
\end{verbatim}

\section{Others}

Other items such as Equations, Figures, Tables and References are produced in
the standard \LaTeX\ typesetting.

\starttwocolumn
\bibliography{compling_style}

\end{document}

### 2019-01-13 Publication/tex_manuscript/manuscript.tex
tex code formatting

--- 2019-01-13 Publication/COLI-manual3.tex
@@
 %Document Head
-\dochead{CLV3 Class File Manual}
+\dochead{Journal of Computational Linguistics}
 
-\runningtitle{How to Use CLV3 \LaTeX\ Class File}
+\runningtitle{Prediction of Legitimate Scientific Writing, and Imitation of Science Via Programmatic Characterization of Written Language}
 
-\runningauthor{Odi\'e N. Gementera}
+\runningauthor{Russell J. Jarvis}
 
@@
 
-\title{How to Use CLV3 \LaTeX\ Class File}
+\title{Prediction of Legitimate Scientific Writing, and Imitation of Science Via Programmatic Characterization of Written Language}
 
-\author{Odi\'e N. Gementera\thanks{PITC Building, Pascor Drive, Sto. Ni\~no, Para\~naque City, 1700 Philippines. E-mail: o.gementera@spi-bpo.com.}}
+\author{Russell J. Jarvis\thanks{PITC Building, Pascor Drive, Sto. Ni\~no, Para\~naque City, 1700 Philippines. E-mail: o.gementera@spi-bpo.com.}}
 \affil{Publishing / SPi}
@@
 
-This document applies to version 3 of CL class file. Prior style files such as 
-``{\tt cl.sty}'' and ``{\tt coli.sty}'' do not have all of the features 
-described here. It is assumed that the user has a basic knowledge of \LaTeX\ 
-typesetting commands.
+Non-scientific writing typically exceeds genuine scientific writing in one important criteria: in contrast to genuine science non-science ideas are often expressed using a lower complexity and more engaging writing style.
+However, multiple stake holders could benefit if science was more often communicated using a lower complexity expression of ideas.
+Knowledge would be more readily mobilized and transferred into public awareness, also, and machine readability and machine organization of factual information derived from journal articles should also occur more readily.
 
-\section{Class File Options}
+We believe non-science writing occupies a style niche, that academic science writing should also occupy.
+We show that we can blindly predict the status of writing: popular culture writing, opinionative writing, and traditional science, by using machine learning to classify the different writing types.
+By predicting which of the several different writing types any writing piece occupies, we are able to characterize among different writing niches.
 
-There are several options that can be used to switch the mode of MIT2 from normal 
-article to manuscript style, or to different layout styles. This is specified in 
-the usual \LaTeX\ way by declaring:
+Objectively describing the different character of the different writing styles will allow us to prescribe how, to shift academic science writing into a more accessible niche, where science can more aggressively compete with pseudo-science, and blogs, facilitating greater knowledge transference, at a moment in history when public awareness is critically at stake.
+
+\section{Methods}
+
+We built a web-scraping and written text analysis infrastructure by extending many existing Free and Open Source (FOS) tools.
+The Web scrapping interface employs several common python modules, chief among those was: Google Scrape, Beautiful Soup and Selenium.
+The Text analysis infrastructure was based on the two substantial code bases Text-stat, which contained measures of text reading level (complexity), and NLTK (the Natural Language Processing Tool Kit), which contained measures of text subjectivity, and sentiment type.
+
+The scraping, and analysis work we performed, rested on top of a large hierarchy of software dependencies.
+However, it is increasingly well understood, that, dependency heavy software stacks act as a significant impediment to investigating or reproducing any product of digital, scholary research.
+In order to address this problem and to enhance the reproducibility of our approach, we created the necessary web-scrapping, and analysis infrastructure inside a dedicated Docker Container.
+
+Reproducibility is burdened by the technical task of satisfying each software dependencies necessary to recreate a digital scientific experiment.
+Our position, of starting with from a cloned software environment, will mitigate, the burden of duplicating our digital research environment.
+That is why we have used a Docker file, and associated Docker container together, as they act as self-documenting and extremely portable software environment clone.
+
+Initially we created two different, unrelated and broad ranging lists of scientific queries.
+The first type of query was predominantly cultural in nature, or world view related.
+The second set of queries represented gains in knowledge about physical entities or physical processes in the world.
+We were interested in scientific, and pseudo-scientific writing.
+
+There were two types of writing that we actively excluded from our analysis, those were websites expressed in a non-English language, and also websites, that were highly commercial in nature.
+These were websites advertisements, of consumer goods, and online shopping generally.
+These websites, utilizing wording, that significantly biases text stat metrics.
+Webpages of less than 400 words, were most often advertisements, and websites
+Non English, websites were excluded for the simple reason that they are not amenable to Textstat, and NLTK tools, however, even if this was not the case, it is also known, that there are  significant differences in per-word information entropy between different natural languages.
+
+\subsection{Search Engine Queries:}
+The first two lists of queries were chosen to be belong to an overt set of exclusively scientific or cultural search terms. A third list of terms was designed to be deliberately ambiguous.
+
+\subsection{Science Queries:}
+The three lists of search engine queries were as implemented as follows: science engine queries: 'evolution', 'photo-sysnthesis' ,'Transgenic', 'GMO', 'climate change', 'cancer', 'Vaccines', 'Genetically Modified Organism', ‘differential equation’,"psycho-physics","soma”
+
+Cultural queries were as follows: 'reality TV', 'prancercise philosophy', 'play dough delicious deserts', 'unicorn versus brumby', 'football soccer' , god fearing.
+
+As discussed we also designed ambiguous queries which were equally likely return content that was either scientific, or non scientific in nature.
+The reason for doing this was to provide a challenge for the classification algorithm.
+
+\subsection{Ambiguous Queries, were as follows:}
+
+"the singularity","skynet","","killer robot","franken-science","Frankenstein,”the God Delusion","god does not play dice", "the selfish gene","political science", ", "requim for a spike"
+
+After scraping across the two different lists were performed, the resulting queries were filtered, according to specific sets of criteria.
+As stated previously, we discarded from our analysis, web pages that were not written in English, since we did not have the necessary tools, to analyze them.
+
+Text Metrics:
+A list of metrics applied to downloaded corpus include: TextStat, which was used to measure word complexity (an average of several important word complexity metrics, such as the Gunning Fog measure of reading level), LZW compression-ratio, de-compression ratio, sentiment analysis, subjectivity analysis, and page rank.
+
+Compression ratios were used to investigate the notion, that well written scientific writing, might simply be lower in information entropy, and an information theoretic analysis, can be used to both to better characterize, and corroborate the findings of other reading word complexity metrics
+
+\subsection{Reference Texts:}
+
+Some reference texts were used, as a means of providing contrast, and context, to data points, among our web scraping derived corpus.
+The Upgoer5 is a library, of scientific texts, written with the aid of a text editor, which imposes, that output documents are exclusively comprised by, only the 10,000 most commonly occurring English words.
+
+The Post Modern Essay Generator (PMEG), embodies an artificial English synthesis technique.
+Documents that are output from the website, consist of sentences that obey the rules of written English, however there are no restraints governing the semantic conceptual references in the sentences.
+If any particular sentence in a PMEG document, embodies an objective meaning, it is only by chance.
+Output from PMEG reads as highly coded, and vague.
+
+The reference data points in some ways provide further validation to the existing text metric tools, as we needed to verify that word readability metrics provided results that were consistant with prior assumptions about known texts.
+For instance, the corpus derived from upgoer editor, should require a very low reading grade level to understand.
+Texts, from the PMEG should require a very high reading level to understand, and cumulative entropy of such texts should be high.
 
@@
 
-\section{Title Page}
+\section{Results}
 

### 2019-01-13 Publication/tex_manuscript/manuscript.tex
tex code formatting

@@
 
-\author{Russell J. Jarvis\thanks{PITC Building, Pascor Drive, Sto. Ni\~no, Para\~naque City, 1700 Philippines. E-mail: o.gementera@spi-bpo.com.}}
-\affil{Publishing / SPi}
+\author{Russell J. Jarvis\thanks{PITC Building, Pascor Drive, Sto. Ni\~no, Para\~naque City, 1700 Philippines. E-mail: rjjarvis@asu.edu.}}
+\affil{School of Life Sciences ASU}
 
@@
 \begin{abstract}
-This article describes how to use the ``CLV3'' class file, developed by {\sf SPi},
-to produce typeset papers based on Computer Linguistics typesetting specifications
-for submission to MIT. This document was produced using ``{\tt clv3}'' class file
-and will be modified whenever there is an update in the layout specifications.
+This article describes how we scrapped a wide variety of written word from the internet, and then analysed scrapped samples, in order to better charecterize the readability of scientific and non scientific writings.
 \end{abstract}

### 2019-01-15 Examples/pickle_reader.py
R code for spam/ham analysis

@@ -1,0 +1,5 @@
+import pandas as pd
+
+def read_pickle_file(file):
+    pickle_data = pd.read_pickle(file)
+    return pickle_data

### 2019-01-15 Examples/r_analysis.R

@@ -1,0 +1,4 @@
+
+require("reticulate")
+source_python("pickle_reader.py")
+pickle_data <- read_pickle_file("scraped.p")

### 2019-01-16 Examples/get_titles_from_csv_snippets.py
dev added in methods for labeling of data

@@ -1,0 +1,57 @@
+import os
+import csv
+import glob
+import glob
+from natsort import natsorted, ns
+import pprint
+import numpy as np
+import os
+
+import matplotlib.pyplot as plt
+import seaborn as sns
+import pandas as pd
+import numpy as np
+import math as math
+from pylab import rcParams
+
+import numpy as np
+import matplotlib.pyplot as plt
+
+from mpl_toolkits.mplot3d import Axes3D
+from sklearn.cluster import KMeans
+from sklearn import datasets
+import seaborn as sns; sns.set()  # for plot styling
+
+import pickle
+from SComplexity.analysis import Analysis
+import pandas as pd
+
+from habanero import Crossref
+cr = Crossref()
+#from habanero import Crossref
+#[ z['DOI'] for z in x['message']['items'] ]
+#[ z['issn'] for z in x['message']['items'] ]
+
+
+#cr = Crossref()
+##
+# This file can be used to show, that K-Means clustering
+# a type of unsupervised classifier, can predict if something is a wikipedia article
+# or not pretty well.
+# It's my opinion that, the classifier could probably predict mainstream science or psuedo science too,
+# given enough dimensions to seperate the clustered data points over.
+##
+
+FILES = natsorted(glob.glob(str(os.getcwd())+'/*.csv'))
+contents = []
+titles = {}
+for csvfile in FILES:
+     with open(csvfile, 'rt') as csvfile:
+         #spamreader = csv.reader(csvfile, delimiter=' ', quotechar='|')
+         contents.append(csv.reader(csvfile))
+         for row in contents[-1]:
+              
+              #if 'title' in row:
+              print(row[-2])
+              titles[row[-2]] = row[-2]
+         #print(contents[-1])

### 2019-01-16 Publication/tex_manuscript/manuscript.tex
dev changes

@@
 
-Non-scientific writing typically exceeds genuine scientific writing in one important criteria: in contrast to genuine science non-science ideas are often expressed using a lower complexity and more engaging writing style.
-However, multiple stake holders could benefit if science was more often communicated using a lower complexity expression of ideas.
-Knowledge would be more readily mobilized and transferred into public awareness, also, and machine readability and machine organization of factual information derived from journal articles should also occur more readily.
+Non-scientific writing typically exceeds genuine scientific writing in one important criteria: in contrast to genuine science non-science ideas are often expressed using a less complex more engaging writing style.
+Yet, multiple stake holders could benefit if science was communicated using a less complex expression of ideas.
+Using less complicated science writing, knowledge could be more readily transferred into public awareness, also, and machine reading machine organization, and machine action on factual information derived from journal articles could occur more readily.
 
@@
 The second set of queries represented gains in knowledge about physical entities or physical processes in the world.
-We were interested in scientific, and pseudo-scientific writing.
+We were interested in scientific, and pseudo-scientific writing.\\
 
@@
 These websites, utilizing wording, that significantly biases text stat metrics.
-Webpages of less than 400 words, were most often advertisements, and websites
+Webpages of less than 400 words, were most often advertisements, and websites of a comercial nature such as Amazon shopping.\\
+
 Non English, websites were excluded for the simple reason that they are not amenable to Textstat, and NLTK tools, however, even if this was not the case, it is also known, that there are  significant differences in per-word information entropy between different natural languages.
@@
 
-\subsection{Science Queries:}
+\subsubsection{Science Queries:}
 The three lists of search engine queries were as implemented as follows: science engine queries: 'evolution', 'photo-sysnthesis' ,'Transgenic', 'GMO', 'climate change', 'cancer', 'Vaccines', 'Genetically Modified Organism', ‘differential equation’,"psycho-physics","soma”
 
-Cultural queries were as follows: 'reality TV', 'prancercise philosophy', 'play dough delicious deserts', 'unicorn versus brumby', 'football soccer' , god fearing.
+\subsubsection{Cultural queries were as follows:} 'reality TV', 'prancercise philosophy', 'play dough delicious deserts', 'unicorn versus brumby', 'football soccer' , god fearing.
 
@@
 
-\subsection{Ambiguous Queries, were as follows:}
+\subsubsection{Ambiguous Queries, were as follows:}
 
@@
 
-Text Metrics:
+\subsection{Text Metrics:}
 A list of metrics applied to downloaded corpus include: TextStat, which was used to measure word complexity (an average of several important word complexity metrics, such as the Gunning Fog measure of reading level), LZW compression-ratio, de-compression ratio, sentiment analysis, subjectivity analysis, and page rank.
@@
 \section{Results}
+
+We created a total list all of the different queries obtained, from combining both the list of cultural queries, and scientific queries, and then applied such queries exclusively to the Wikipedia, search interface.
+We take the result of evaluating this pool of queries, and then plot the resulting pool of queries versus page rank.
+The Wikipedia, actually showed a small but consistant preference for web pages of higher complexity.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.7\linewidth]{screenshot001}
+	\caption{}
+	\label{fig:figure1}
+\end{figure}
+
+The plots below may appear to look a bit unprofessional, as not all data points have error bars.
+The reason for this, is pandas+seaborne allows you to plot on the same axis multiple sample data points, and single sampled data points.
+Only of the five mentioned search engines was made to sample beyond page rank 10, but all five sampled under page rank 10.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.7\linewidth, height=0.7\textheight]{figure2}
+	\caption{}
+	\label{fig:figure2}
+\end{figure}
+
+The same plot but with mean and std deviation plots when multiple samples per page rank are available.
+When we plotted the Wikipedia queries, where reading (text-stat standard) level is instead plotted against page rank, we again see that there is a slight trend towards increasing text complexity with decreasing page rank.
+
+If instead we consider how resistant Wikipedia pages are to compression, we see that low page rank pages, are more resistant to compression.
+This finding recapitulates the same result as the above figure, where increasing Wikipedia page rank slightly decreases text complexity.
+
+When aggregated search results between all possible search engines, and then plotting page rank versus complexity, for particular types of search terms, there was a strong positive correlation between page rank, and reading level.
+
+In the case of GMO, and Genetically Modified Organism, positive increasing trends where observed
 

### 2019-01-16 Examples/against_references.py

@@ -12,192 +12,27 @@ import numpy as np
 import math as math
 from pylab import rcParams
 
-import numpy as np
-import matplotlib.pyplot as plt
-
-from mpl_toolkits.mplot3d import Axes3D
-from sklearn.cluster import KMeans
-from sklearn import datasets
-import seaborn as sns; sns.set()  # for plot styling
 
 import pickle
 from SComplexity.analysis import Analysis
 import pandas as pd
 
-from habanero import Crossref
-cr = Crossref()
-#from habanero import Crossref
-#[ z['DOI'] for z in x['message']['items'] ]
-#[ z['issn'] for z in x['message']['items'] ]
-
-
-#cr = Crossref()
-##
-# This file can be used to show, that K-Means clustering
-# a type of unsupervised classifier, can predict if something is a wikipedia article
-# or not pretty well.
-# It's my opinion that, the classifier could probably predict mainstream science or psuedo science too,
-# given enough dimensions to seperate the clustered data points over.
-##
-
 FILES = natsorted(glob.glob(str(os.getcwd())+'/results_dir/*.p'))
-
+# This cannot properly handle wiki files
 A = Analysis(FILES, min_word_length = 200)
 urlDats = A.cas()
 print(urlDats)
 
-scraped_new = list(filter(lambda url: str('query') in url.keys(), urlDats))
-with open('scraped_new.p','wb') as f:
-    pickle.dump(scraped_new,f)
+scraped = list(filter(lambda url: str('query') in url.keys(), urlDats))
 
-#by_query[str('science')]['urlDats'] = list(filter(lambda url: url['query'] in science_keys, scraped))
-for s in scraped_new:
-    print(s['query'])
-import pdb;
-pdb.set_trace()
-
-'''
-reference = A.get_reference_web()
-dfr = pd.DataFrame(reference)
-
-labels = [ w['link'] for w in reference ]
-by_query['reference'] = {}
-#by_query['reference']['sp'] = [ w['sp'] for w in reference ]
-by_query['reference']['standard'] = [ w['standard'] for w in reference ]
-by_query['reference']['info_density'] = [ w['info_density'] for w in reference ]
-
[…]

### 2019-01-16 SComplexity/analysis.py

@@ -38,9 +38,15 @@ class Analysis(object):
 
     def cas(self):
         # Do in parallel as it is 2018
-        grid = db.from_sequence(self.files,npartitions=8)
-        urlDats = list(db.map(self.convert_and_score,grid).compute())
+    
+        pgrid = db.from_sequence(self.files,npartitions=8)
+        urlDats = list(db.map(self.convert_and_score,pgrid).compute())
+        # just kidding need to do a serial debug often times, regardless of parallel speed up.
+        #urlDats = list(map(self.convert_and_score,self.files))
+        urlDats = [ url for url in urlDats if type(url) is not type(None) ]
+        #urlDats = list(filter(lambda url: type(url) != None, urlDats))
         urlDats = list(filter(lambda url: len(list(url))>3, urlDats))
+
         urlDats = list(filter(lambda url: len(list(url.keys()))>3, urlDats))
         # urlDats = list(filter(lambda url: str('penalty') in url.keys(), urlDats))
         if type(self.urlDats) is not type(None):

### 2019-01-16 SComplexity/authors.py

@@ -1,8 +1,153 @@
 #import scholar
+#from SComplexity.
+#!pip install -e +git https://github.com/ckreibich/scholar.py
+import sys
+from scholar_scrape import scholar
+import pandas as pd
+
+#sys.version_info[0] == 3:
+unicode = str # pylint: disable-msg=W0622
+encode = lambda s: unicode(s) # pylint: disable-msg=C0103                                                                                                                                                                                '''
+
+def csv(querier, header=False, sep='|'):
+    articles = querier.articles
+    results = []
+    for art in articles:
+        result = art.as_csv(header=header, sep=sep)
+        results.append(result)
+        print(encode(result))
+        header = False
+    return results
+from delver import Crawler
+C = Crawler()
+import requests
+
+from SComplexity.crawl import collect_pubs
 from SComplexity.scholar_scrape import scholar
+
+import io
+
+from delver import Crawler
+C = Crawler()
+import requests
+
+
+import io
+
+import selenium
+
+from selenium import webdriver
+from pyvirtualdisplay import Display
+
+display = Display(visible=0, size=(1024, 768))
+display.start()
+
+
+#from StringIO import StringIO
+
+from pdfminer.pdfinterp import PDFResourceManager, PDFPageInterpreter
+from pdfminer.converter import TextConverter
+from pdfminer.layout import LAParams
+from pdfminer.pdfpage import PDFPage
+import os
+import sys, getopt
+from io import StringIO
+
+from selenium.webdriver.firefox.options import Options
+
+import re
+from bs4 import BeautifulSoup
+import bs4 as bs
+import urllib.request
+from io import StringIO
+import io
+
+display = Display(visible=0, size=(1024, 768))
+display.start()
+
+
+from selenium.webdriver.firefox.options import Options
+
+import re
+from bs4 import BeautifulSoup
+
+
+import PyPDF2
+from PyPDF2 import PdfFileReader
+import textract
+
+def html_to_author(content,link):
+    soup = BeautifulSoup(content, 'html.parser')
+
+    page = urllib.request.urlopen(url)
+    soup = BeautifulSoup(page, 'lxml')
+    mydivs = soup.findAll("h3", { "class" : "gsc_1usr_name"})
+    outputFile = open('sample.csv', 'w', newline='')
+    outputWriter = csv.writer(outputFile)
+    for each in mydivs:
+        for anchor in each.find_all('a'):
+            print(anchor.text)
+
+
+    #strip HTML
[…]

### 2019-01-16 SComplexity/crawl.py

@@ -34,10 +34,20 @@ display.start()
 #profile.set_preference("javascript.enabled", True)
 #driver = webdriver.Firefox(profile = profile)
 
-from selenium.webdriver.firefox.options import Options
-options = Options()
-options.headless = True
-driver = webdriver.Firefox(options=options) 
+#from selenium.webdriver.firefox.options import Options
+#options = Options()
+#options.headless = True
+#driver = webdriver.Firefox(options=options)
+chrome_options = webdriver.ChromeOptions()
+chrome_options.add_argument('--no-sandbox')
+chrome_options.add_argument('--headless')
+chrome_options.add_argument('--disable-gpu')
+#driver = webdriver.Chrome(chrome_options=chrome_options)
+driver = webdriver.Chrome(executable_path='/usr/local/bin/chromedriver',chrome_options=chrome_options)
+
+driver.implicitly_wait(10)
+from selenium.common.exceptions import NoSuchElementException
+
 
 import pandas as pd
 import pycld2 as cld2

### 2019-01-16 SComplexity/scrape.py

@@ -7,10 +7,6 @@
 
 # Patrick McGurrin
 # patrick.mcgurrin@gmail.com
-import selenium
-from pyvirtualdisplay import Display
-from selenium import webdriver
-#from fake_useragent import UserAgent
 from numpy import random
 import os
 from bs4 import BeautifulSoup
@@ -30,16 +26,20 @@ from pdfminer.converter import  TextConverter
 
 from SComplexity.crawl import convert_pdf_to_txt
 from SComplexity.crawl import print_best_text
-from delver import Crawler
-C = Crawler()
-import requests
-#import duckduckgo
-#from numba import jit
-#import scholar_scrape
 from SComplexity.crawl import collect_pubs
 from SComplexity.scholar_scrape import scholar
 
+from delver import Crawler
+C = Crawler()
+import requests
+
+
 import io
+
+import selenium
+
+from selenium import webdriver
+from pyvirtualdisplay import Display
 
 display = Display(visible=0, size=(1024, 768))
 display.start()
@@ -55,9 +55,17 @@ from io import StringIO
 import io
 
 
-options = Options()
-options.headless = True
-driver = webdriver.Firefox(options=options)
+#options = Options()
+#options.headless = True
+chrome_options = webdriver.ChromeOptions()
+chrome_options.add_argument('--no-sandbox')
+chrome_options.add_argument('--headless')
+chrome_options.add_argument('--disable-gpu')
+driver = webdriver.Chrome(executable_path='/usr/local/bin/chromedriver',chrome_options=chrome_options)
+#driver = webdriver.Chrome(chrome_options=chrome_options)
+driver.implicitly_wait(10)
+from selenium.common.exceptions import NoSuchElementException
+
 
 
 rsrcmgr = PDFResourceManager()
@@ -70,24 +78,82 @@ interpreter = PDFPageInterpreter(rsrcmgr, device)
 
 
 
+#from pyPdf import PdfFileReader
 
-def pdf_to_txt(content):
+#from StringIO import StringIO
+
+from pdfminer.pdfinterp import PDFResourceManager, PDFPageInterpreter
+from pdfminer.converter import TextConverter
+from pdfminer.layout import LAParams
+from pdfminer.pdfpage import PDFPage
+import os
+import sys, getopt
+from io import StringIO
+
+#converts pdf, returns its text content as a string
+def pdf_to_txt_(infile):#, pages=None):
+    #if not pages:
+    pagenums = set()
+
+    output = StringIO()
[…]

### 2019-01-16 SComplexity/t_analysis.py

@@ -45,6 +45,7 @@ from nltk.sentiment import SentimentAnalyzer
 
 from textstat.textstat import textstat
 
+from nltk.corpus import stopwords
 
 
 from SComplexity.utils import black_string, english_check, comp_ratio, clue_words, clue_links, publication_check
@@ -61,69 +62,76 @@ def text_proc(corpus, urlDat = {}, WORD_LIM = 100):
     #    urlDat['pub'] = pub
     #print(type(corpus),corpus)
     #r emove unreadable characters
-    corpus = corpus.replace("-", " ") #remove characters that nltk can't read
-    textNum = re.findall(r'\d', corpus) #locate numbers that nltk cannot see to analyze
-    tokens = word_tokenize(corpus)
-    tokens = [w.lower() for w in tokens] #make everything lower case
-    # the kind of change that might break everything
-    urlDat['wcount'] = textstat.lexicon_count(str(tokens))
-    word_lim = bool(urlDat['wcount']  > WORD_LIM)
+    if type(corpus) is str:
+        corpus = corpus.replace("-", " ") #remove characters that nltk can't read
+        textNum = re.findall(r'\d', corpus) #locate numbers that nltk cannot see to analyze
+        tokens = word_tokenize(corpus)
 
-    # Word limits can be used to filter out product merchandise websites, which otherwise dominate scraped results.
-    # Search engine business model is revenue orientated, so most links will be for merchandise.
+        stop_words = stopwords.words('english')
+        #We create a list comprehension which only returns a list of words #that are NOT IN stop_words and NOT IN punctuations.
+    
+        tokens = [ word for word in tokens if not word in stop_words]
+        tokens = [w.lower() for w in tokens] #make everything lower case
 
-    urlDat['publication'] = publication_check(str(tokens))
-    urlDat['english'] = english_check(str(tokens))
-    urlDat['clue_words'] = clue_words(str(tokens))
-    urlDat['clue_links'] = clue_links(urlDat['link'])
+        # the kind of change that might break everything
+        urlDat['wcount'] = textstat.lexicon_count(str(tokens))
+        word_lim = bool(urlDat['wcount']  > WORD_LIM)
 
-    # The post modern essay generator is so obfuscated, that ENGLISH classification fails, and this criteria needs to be relaxed.
-    not_empty = bool(len(tokens) != 0)
-    print(not_empty,urlDat['english'],word_lim)
-    if urlDat['english']==False:
-        pass
+        # Word limits can be used to filter out product merchandise websites, which otherwise dominate scraped results.
[…]

### 2019-01-30 Publication/tex_manuscript/manuscript.tex
update writing

@@
 
-\runningtitle{Prediction of Legitimate Scientific Writing, and Imitation of Science Via Programmatic Characterization of Written Language}
+\runningtitle{Science Accessibility Project}
 
@@
 
-\title{Prediction of Legitimate Scientific Writing, and Imitation of Science Via Programmatic Characterization of Written Language}
+\title{Science Accessibility Project}
 
-\author{Russell J. Jarvis\thanks{PITC Building, Pascor Drive, Sto. Ni\~no, Para\~naque City, 1700 Philippines. E-mail: rjjarvis@asu.edu.}}
+\author{Russell J. Jarvis\thanks{Tempe, ASU. E-mail: rjjarvis@asu.edu.}}
 \affil{School of Life Sciences ASU}
@@
 
+\subsection{}keywords} 
+Bag of words analysis, naive Bayes.
+
 \section{Introduction}
+# Science Accessibility Project
+## Motivation for the Science Accessibility Project
+Non-scientific writing typically exceeds genuine scientific writing in one important criteria: in contrast to genuine science non-science ideas are often expressed with a more accessible writing style.
+We believe non-science writing occupies a more accessible style niche, that academic science writing should also occupy.
+We show that we can use machine learning to predict the status of writing: popular culture writing, opinionative writing, and traditional science, by first scrapping a large variety of web documents, and then classifying among the different writing types.
+By predicting which of the several different writing types any writing piece occupies, we are able to characterize among different writing niches.\\
+\\
+Multiple stake holders can benefit when science is communicated with lower complexity expression of ideas.
+With lower complexity science writing, knowledge would be more readily transferred into public awareness, additionally, digital organization of facts derived from journal articles would occur more readily, as successful machine comprehension of documented science would likely occur with less human intervention.\\
+\\
+Objectively describing the different character of the different writing styles will allow us to prescribe how, to shift academic science writing into a more accessible niche, where science can more aggressively compete with pseudo-science, and blogs, facilitating greater knowledge transference, at a moment in history when public awareness is critically at stake.
+
+## Machine Estimation of Writing Complexity.
+The accessibility of written word can be approximated by a computer program that reads over the text, and guesses the mental difficulty, associated with comprehending a written document.
+The computer program maps reading difficult onto a quantity that represents the number of years of schooling needed to decode the language in the document.
+For convenience, we can refer to the difficulty associated with the text as the 'complexity' of the document.
+
+\section{Introduction Old}
 
@@
 
-\begin{figure}
-	\centering
-	\includegraphics[width=0.7\linewidth]{screenshot001}
-	\caption{}
-	\label{fig:figure1}
-\end{figure}
+%\begin{figure}
+%	\centering
+%	\includegraphics[width=0.7\linewidth]{screenshot001}
+%	\caption{}
+%	\label{fig:figure1}
+%\end{figure}
+
+%
 
@@
 
-\begin{figure}
-	\centering
-	\includegraphics[width=0.7\linewidth, height=0.7\textheight]{figure2}
-	\caption{}
-	\label{fig:figure2}
-\end{figure}
+%\begin{figure}
+%	\centering
+%	\includegraphics[width=0.7\linewidth, height=0.7\textheight]{figure2}
+%	\caption{}
+%	\label{fig:figure2}
+%\end{figure}
+%
 

### 2019-01-31 Examples/use_analysis.py
changes

@@ -43,7 +43,11 @@ cr = Crossref()
 FILES = natsorted(glob.glob(str(os.getcwd())+'/results_dir/*.p'))
 
 A = Analysis(FILES, min_word_length = 200)
+references = A.get_reference_web()
+#import pdb
+#pdb.set_trace()
 urlDats = A.cas()
+
 print(urlDats)
 
 scraped_new = list(filter(lambda url: str('query') in url.keys(), urlDats))
@@ -53,8 +57,8 @@ with open('scraped_new.p','wb') as f:
 #by_query[str('science')]['urlDats'] = list(filter(lambda url: url['query'] in science_keys, scraped))
 for s in scraped_new:
     print(s['query'])
-import pdb;
-pdb.set_trace()
+#import pdb;
+#pdb.set_trace()
 
 '''
 reference = A.get_reference_web()

### 2019-01-31 Examples/word_cloud.py

@@ -1,0 +1,59 @@
+
+import os
+
+from os import path
+from wordcloud import WordCloud
+import matplotlib
+matplotlib.use('Agg') 
+# get data directory (using getcwd() is needed to support running example in generated IPython notebook)
+d = path.dirname(__file__) if "__file__" in locals() else os.getcwd()
+
+# Read the whole text.
+#text = open(path.join(d, 'constitution.txt')).read()
+#references.p  scraped_new.p
+import pickle
+texts = pickle.load(open('scraped_new.p','rb'))
+#import pdb
+#pdb.set_trace()
+#for t in texts:
+pre_science = ''
+pre_not_science = ''
+for t in texts:
+    if t['publication'][0] == False:
+        for s in t['tokens']: pre_not_science+=str(' ')+s
+    elif t['publication'][0] == True:
+        for s in t['tokens']: pre_science+=str(' ')+s
+
+# Generate a word cloud image
+wordcloud = WordCloud().generate(pre_science)
+print(wordcloud)
+# Display the generated image:
+# the matplotlib way:
+import matplotlib.pyplot as plt
+
+plt.imshow(wordcloud, interpolation='bilinear')
+plt.axis("off")
+
+# lower max_font_size
+#wordcloud = WordCloud(max_font_size=40).generate(text)
+#plt.figure()
+#plt.imshow(wordcloud, interpolation="bilinear")
+#plt.axis("off")
+plt.savefig('science_cloud.png')# Generate a word cloud image
+
+
+
+wordcloud = WordCloud().generate(pre_not_science)
+
+# Display the generated image:
+# the matplotlib way:
+import matplotlib.pyplot as plt
+plt.imshow(wordcloud, interpolation='bilinear')
+plt.axis("off")
+
+# lower max_font_size
+wordcloud = WordCloud(max_font_size=40).generate(pre_not_science)
+plt.figure()
+plt.imshow(wordcloud, interpolation="bilinear")
+plt.axis("off")
+plt.savefig('not_science_cloud.png')

### 2019-01-31 SComplexity/t_analysis.py

@@ -48,7 +48,8 @@ from textstat.textstat import textstat
 from nltk.corpus import stopwords
 
 
-from SComplexity.utils import black_string, english_check, comp_ratio, clue_words, clue_links, publication_check
+# english_check
+from SComplexity.utils import black_string, comp_ratio, clue_words, clue_links, publication_check
 
 DEBUG = False
 #from numba import jit
@@ -76,20 +77,20 @@ def text_proc(corpus, urlDat = {}, WORD_LIM = 100):
         # the kind of change that might break everything
         urlDat['wcount'] = textstat.lexicon_count(str(tokens))
         word_lim = bool(urlDat['wcount']  > WORD_LIM)
-
+        urlDat['tokens'] = tokens 
         # Word limits can be used to filter out product merchandise websites, which otherwise dominate scraped results.
         # Search engine business model is revenue orientated, so most links will be for merchandise.
 
         urlDat['publication'] = publication_check(str(tokens))
-        urlDat['english'] = english_check(str(tokens))
+        #urlDat['english'] = english_check(str(tokens))
         urlDat['clue_words'] = clue_words(str(tokens))
         urlDat['clue_links'] = clue_links(urlDat['link'])
-
+        
         # The post modern essay generator is so obfuscated, that ENGLISH classification fails, and this criteria needs to be relaxed.
         not_empty = bool(len(tokens) != 0)
-        print(not_empty,urlDat['english'],word_lim)
-        if urlDat['english']==False:
-            pass
+        #print(not_empty,urlDat['english'],word_lim)
+        #if urlDat['english']==False:
+        #    pass
         #print(str(tokens))
 
         if not_empty and word_lim: #  and server_error:

### 2019-01-31 setup.py

@@ -5,7 +5,7 @@ from distutils.core import setup
 import setuptools
 setup(name='scomplexity',
       version='1.0',
-      description='heavily applied scrapping, crawling and language analysis, tightly coupled with the goal of analysing scientific discourse',
+      description='heavily applied scraping, crawling and language analysis, tightly coupled with the goal of analysing scientific discourse',
       author='various',
       author_email='don_t_email_we_are_on_github@gmail.com',
       url='https://github.com/russelljjarvis/WordComplexityPython',

### 2019-02-01 Examples/use_analysis.py
dev changes

@@ -43,7 +43,10 @@ cr = Crossref()
 FILES = natsorted(glob.glob(str(os.getcwd())+'/results_dir/*.p'))
 
 A = Analysis(FILES, min_word_length = 200)
-references = A.get_reference_web()
+try:
+    references = A.get_reference_web()
+except:
+    pass
 #import pdb
 #pdb.set_trace()
 urlDats = A.cas()
@@ -86,7 +89,7 @@ dfs = pd.DataFrame(scraped_new)
 
 dfs = dfs[~dfs['link'].isin(['https://www.youtube.com/'])]
 dfs = dfs[~dfs['link'].isin(['https://www.walmart.com'])]
-dfs = dfs[~dfs['link'].isin(['https://foundation.wikimedia.org/wiki/Privacy_policy'])]
+dfs = dfs[~dfs['link'].isin(['https://foundation.wikimedia.org/wiki/Privacy_policy'])] 
 
 #wikipedia = wikipedia[wikipedia['link']==str('https://foundation.wikimedia.org/wiki/Privacy_policy')]
 wikipedia = dfs[dfs['se']==str('wikipedia')]
@@ -189,7 +192,9 @@ accuracy_score(y_test.values, y_predict)
 '''
 
 #scraped = scraped_new
+scraped_new  = [ w['sp'] for w in scraped_new if str('sp') in w.keys() ]
 sps = [ w['sp'] for w in scraped_new ]
+
 fogss = [ w['gf'] for w in scraped_new ]
 infos = [ w['info_density'] for w in scraped_new ]
 ranks = [ w['page_rank'] for w in scraped_new ]

### 2019-02-01 Examples/word_cloud.py

@@ -4,56 +4,196 @@ import os
 from os import path
 from wordcloud import WordCloud
 import matplotlib
-matplotlib.use('Agg') 
-# get data directory (using getcwd() is needed to support running example in generated IPython notebook)
-d = path.dirname(__file__) if "__file__" in locals() else os.getcwd()
+matplotlib.use('Agg')
 
-# Read the whole text.
-#text = open(path.join(d, 'constitution.txt')).read()
-#references.p  scraped_new.p
+
+import seaborn as sns
+import matplotlib.pyplot as plt
+import pandas as pd
+
+import matplotlib.pyplot as plt
+from SComplexity import get_bmark_corpus as gbc
+
 import pickle
 texts = pickle.load(open('scraped_new.p','rb'))
-#import pdb
-#pdb.set_trace()
-#for t in texts:
+references = pickle.load(open('references.p','rb'))
+
 pre_science = ''
 pre_not_science = ''
+wiki = ''
+
 for t in texts:
-    if t['publication'][0] == False:
+    if t['science'] == False:
         for s in t['tokens']: pre_not_science+=str(' ')+s
-    elif t['publication'][0] == True:
+    elif t['science'] == True:
         for s in t['tokens']: pre_science+=str(' ')+s
+    elif t['wiki'] == True:
+        for s in t['tokens']: wiki+=str(' ')+s
 
-# Generate a word cloud image
-wordcloud = WordCloud().generate(pre_science)
-print(wordcloud)
-# Display the generated image:
-# the matplotlib way:
+
+
+def make_word_clouds(pre_science,pre_not_science,wikis):
+    with open('science.csv', 'w') as f:
+        f.write(pre_science)
+
+    with open('not_science.csv', 'w') as f:
+        f.write(pre_not_science)
+    # Generate a word cloud image
+    wordcloud = WordCloud().generate(pre_science)
+    plt.imshow(wordcloud, interpolation='bilinear')
+    plt.axis("off")
+    plt.savefig('science_cloud.png')# Generate a word cloud image
+
+
+
+    wordcloud = WordCloud().generate(pre_not_science)
+    import matplotlib.pyplot as plt
+    plt.imshow(wordcloud, interpolation='bilinear')
+    plt.axis("off")
+
+    # lower max_font_size
[…]

### 2019-02-01 SComplexity/get_bmark_corpus.py

@@ -18,14 +18,23 @@ import dask.bag as db
 
 
 
-
+from bs4 import BeautifulSoup
 def process(link):
     urlDat = {}
     urlDat['link'] = link
     urlDat['page_rank'] = 'benchmark'
     if str('pdf') not in link:
         content = C.open(link).content
-        buffer = convert(content,urlDat['link'])
+        soup = BeautifulSoup(content, 'html.parser')
+        for script in soup(["script", "style"]):
+            script.extract()    # rip it out
+        text = soup.get_text()
+        #wt = copy.copy(text)
+        #organize text
+        lines = (line.strip() for line in text.splitlines())  # break into lines and remove leading and trailing space on each
+        chunks = (phrase.strip() for line in lines for phrase in line.split("  ")) # break multi-headlines into a line each
+        text = '\n'.join(chunk for chunk in chunks if chunk) # drop blank lines
+        buffer = str(text)
     else:
         pdf_file = requests.get(link, stream=True)
         buffer = convert_pdf_to_txt(pdf_file)
@@ -45,33 +54,7 @@ def get_bmarks():
     the_science_of_writing = str('https://cseweb.ucsd.edu/~swanson/papers/science-of-writing.pdf')
     pmeg = str('http://www.elsewhere.org/pomo/') # Note this is so obfuscated, even the english language classifier rejects it.
     links = [xkcd_self_sufficient,high_standard,the_science_of_writing,pmeg ]
-    print(links)
-    #klpdfp = text_proc(strText,urlDat, WORD_LIM = 100)
-    grid = db.from_sequence(links,npartitions=8)
-    print(grid)
-    urlDats = list(db.map(process,grid).compute())
-    #urlDats.append(klpdfp)
-    print(urlDats)
-    '''
-    royal = '../BenchmarkCorpus/royal.txt'
-    klpd = '../BenchmarkCorpus/planning_document.txt'
-    klpdf = open(klpd)
-    strText = klpdf.read()
-    urlDat = {'link':'local_resource'}
-
-
-
-    klpdr = open(royal)
-    strText = klpdr.read()
-    urlDat = {'link':'local_resource_royal'}
-
-    klpdfr = text_proc(strText,urlDat, WORD_LIM = 100)
-    print(klpdfr)
-    grid = db.from_sequence(links,npartitions=8)
-    urlDats = list(db.map(process,grid).compute())
-    urlDats.append(klpdfp)
[…]

### 2019-02-01 SComplexity/scrape.py

@@ -93,7 +93,7 @@ from io import StringIO
 #converts pdf, returns its text content as a string
 def pdf_to_txt_(infile):#, pages=None):
     #if not pages:
-    pagenums = set()
+    #pagenums = set()
 
     output = StringIO()
     manager = PDFResourceManager()

### 2019-02-01 SComplexity/t_analysis.py

@@ -63,29 +63,39 @@ def text_proc(corpus, urlDat = {}, WORD_LIM = 100):
     #    urlDat['pub'] = pub
     #print(type(corpus),corpus)
     #r emove unreadable characters
-    if type(corpus) is str:
+    if type(corpus) is str and str('privacy policy') not in corpus:
         corpus = corpus.replace("-", " ") #remove characters that nltk can't read
         textNum = re.findall(r'\d', corpus) #locate numbers that nltk cannot see to analyze
         tokens = word_tokenize(corpus)
 
         stop_words = stopwords.words('english')
         #We create a list comprehension which only returns a list of words #that are NOT IN stop_words and NOT IN punctuations.
-    
+
         tokens = [ word for word in tokens if not word in stop_words]
         tokens = [w.lower() for w in tokens] #make everything lower case
 
         # the kind of change that might break everything
         urlDat['wcount'] = textstat.lexicon_count(str(tokens))
         word_lim = bool(urlDat['wcount']  > WORD_LIM)
-        urlDat['tokens'] = tokens 
+        urlDat['tokens'] = tokens
         # Word limits can be used to filter out product merchandise websites, which otherwise dominate scraped results.
         # Search engine business model is revenue orientated, so most links will be for merchandise.
 
-        urlDat['publication'] = publication_check(str(tokens))
+        urlDat['publication'] = publication_check(str(tokens))[1]
         #urlDat['english'] = english_check(str(tokens))
-        urlDat['clue_words'] = clue_words(str(tokens))
-        urlDat['clue_links'] = clue_links(urlDat['link'])
-        
+        urlDat['clue_words'] = clue_words(str(tokens))[1]
+        urlDat['clue_links'] = clue_links(urlDat['link'])[1]
+
+        #print(urlDat   ['clue_words'],urlDat['publication'],urlDat['clue_links'])
+        temp = len(urlDat['clue_words'])+len(urlDat['publication'])+len(urlDat['clue_links'])
+        if temp  > 10 and str('wiki') not in urlDat['link']:
+            urlDat['science'] = True
+        else:
+            urlDat['science'] = False
+
+        if str('wiki') in urlDat['link']:
+            urlDat['wiki'] = True
+            #print(urlDat['science'],urlDat['link'])
         # The post modern essay generator is so obfuscated, that ENGLISH classification fails, and this criteria needs to be relaxed.
         not_empty = bool(len(tokens) != 0)
[…]

### 2019-02-01 SComplexity/utils.py

@@ -157,7 +157,7 @@ def clue_words(check_with):
     str("journal of"),str("abstract"),str("materials and methods"),str("nature"), \
     str("conflict of interest"), str("objectives"), str("significance"), \
     str("published"), str("references"), str("acknowledgements"), str("authors"), str("hypothesis"), \
-    str("nih"),str('article'),str('affiliations')]
+    str("nih"),str('article'),str('affiliations'),str('et al')]
     assume_false = []
     for check in CHECKS:
         if check in check_with:

### 2019-02-02 SComplexity/get_bmark_corpus.py
dev changes

@@ -53,8 +53,18 @@ def get_bmarks():
     high_standard = str('https://elifesciences.org/download/aHR0cHM6Ly9jZG4uZWxpZmVzY2llbmNlcy5vcmcvYXJ0aWNsZXMvMjc3MjUvZWxpZmUtMjc3MjUtdjIucGRm/elife-27725-v2.pdf?_hash=WA%2Fey48HnQ4FpVd6bc0xCTZPXjE5ralhFP2TaMBMp1c%3D')
     the_science_of_writing = str('https://cseweb.ucsd.edu/~swanson/papers/science-of-writing.pdf')
     pmeg = str('http://www.elsewhere.org/pomo/') # Note this is so obfuscated, even the english language classifier rejects it.
-    links = [xkcd_self_sufficient,high_standard,the_science_of_writing,pmeg ]
+    this_manuscript = str('https://www.overleaf.com/read/dqkttvmqjvhn')
+    this_readme = str('https://github.com/russelljjarvis/ScienceAccessibility')
+    links = [xkcd_self_sufficient,high_standard,the_science_of_writing,this_manuscript,this_readme ]
     urlDats = list(map(process,links))
+    for i in range(0,9):
+        pmegs.append(process(pmeg)) # grab this constantly changing page 10 times to get the mean value.
+    urlDats.append(process(pmeg))
+    urlDats[-1]['standard'] = np.mean([p['standard'] for p in pmegs])
+    urlDats[-1]['sp'] = np.mean([p['sp'] for p in pmegs])
+    u#rlDats[-1]['subjectivity'] = np.mean([p['sp'] for p in pmegs])
+    urlDats[-1]['gf'] = np.mean([p['gf'] for p in pmegs])
+
     with open('benchmarks.p','wb') as f:
         pickle.dump(urlDats,f)
     return urlDats

### 2019-02-02 Examples/word_cloud.py
dev changes

@@ -5,7 +5,18 @@ from os import path
 from wordcloud import WordCloud
 import matplotlib
 matplotlib.use('Agg')
-
+import pdb
+import pandas as pd
+from pandas.tools.plotting import table
+#import bokeh
+from bokeh.plotting import figure, output_file, show, ColumnDataSource
+from bokeh.models import HoverTool
+from bokeh.plotting import figure, output_file, show
+#%matplotlib inline
+from bokeh.plotting import show, output_notebook, save
+from bokeh.models import ColumnDataSource, OpenURL, TapTool
+import os
+import numpy as np
 
 import seaborn as sns
 import matplotlib.pyplot as plt
@@ -16,23 +27,41 @@ from SComplexity import get_bmark_corpus as gbc
 
 import pickle
 texts = pickle.load(open('scraped_new.p','rb'))
-references = pickle.load(open('references.p','rb'))
+try:
+    references = pickle.load(open('references.p','rb'))
+    print(references[-1]['standard'])
+except:
+    references = gbc.get_bmarks()
+    pickle.dump(references,open('references.p','wb'))
+#import pdb; pdb.set_trace()
+
 
 pre_science = ''
 pre_not_science = ''
-wiki = ''
+wikis = ''
 
 for t in texts:
     if t['science'] == False:
-        for s in t['tokens']: pre_not_science+=str(' ')+s
+        for s in t['tokens']:
+            pre_not_science+=str(' ')+s
     elif t['science'] == True:
-        for s in t['tokens']: pre_science+=str(' ')+s
-    elif t['wiki'] == True:
-        for s in t['tokens']: wiki+=str(' ')+s
+        for s in t['tokens']:
+            pre_science+=str(' ')+s
+    if str('wiki') in t['link']:
+        for s in t['tokens']:
+            wikis+=str(' ')+s
 
+mean_wiki_pedia = []
+for t in texts:
+    if t['wiki'] == True:
+        if str('standard') in t.keys():
 
+            mean_wiki_pedia.append(t['standard'])
+mwp = np.mean(mean_wiki_pedia)
 
 def make_word_clouds(pre_science,pre_not_science,wikis):
+    import matplotlib.pyplot as plt
+
     with open('science.csv', 'w') as f:
         f.write(pre_science)
 
[…]

### 2019-02-02 SComplexity/get_bmark_corpus.py

@@ -57,12 +57,13 @@ def get_bmarks():
     this_readme = str('https://github.com/russelljjarvis/ScienceAccessibility')
     links = [xkcd_self_sufficient,high_standard,the_science_of_writing,this_manuscript,this_readme ]
     urlDats = list(map(process,links))
+    pmegs = []
     for i in range(0,9):
         pmegs.append(process(pmeg)) # grab this constantly changing page 10 times to get the mean value.
     urlDats.append(process(pmeg))
     urlDats[-1]['standard'] = np.mean([p['standard'] for p in pmegs])
     urlDats[-1]['sp'] = np.mean([p['sp'] for p in pmegs])
-    u#rlDats[-1]['subjectivity'] = np.mean([p['sp'] for p in pmegs])
+    #urlDats[-1]['subjectivity'] = np.mean([p['sp'] for p in pmegs])
     urlDats[-1]['gf'] = np.mean([p['gf'] for p in pmegs])
 
     with open('benchmarks.p','wb') as f:

### 2019-02-02 SComplexity/t_analysis.py

@@ -77,6 +77,8 @@ def text_proc(corpus, urlDat = {}, WORD_LIM = 100):
         # the kind of change that might break everything
         urlDat['wcount'] = textstat.lexicon_count(str(tokens))
         word_lim = bool(urlDat['wcount']  > WORD_LIM)
+
+        ## Remove the search term from the tokens somehow.
         urlDat['tokens'] = tokens
         # Word limits can be used to filter out product merchandise websites, which otherwise dominate scraped results.
         # Search engine business model is revenue orientated, so most links will be for merchandise.
@@ -95,7 +97,9 @@ def text_proc(corpus, urlDat = {}, WORD_LIM = 100):
 
         if str('wiki') in urlDat['link']:
             urlDat['wiki'] = True
-            #print(urlDat['science'],urlDat['link'])
+        else:
+            urlDat['wiki'] = False
+        #print(urlDat['science'],urlDat['link'])
         # The post modern essay generator is so obfuscated, that ENGLISH classification fails, and this criteria needs to be relaxed.
         not_empty = bool(len(tokens) != 0)
         #print(not_empty,urlDat['english'],word_lim)

### 2019-10-17 Examples/use_training.py
JOSS figure and notebook added

@@ -23,9 +23,35 @@ from nltk import pos_tag, sent_tokenize, word_tokenize
 from nltk.corpus import cmudict, stopwords, subjectivity
 import re
 from SComplexity.analysis import Analysis
-from SComplexity.t_analysis import text_proc, perplexity, unigram
+from SComplexity.t_analysis import text_proc, perplexity, unigram_zipf
 
 #from SComplexity.get_bmark_corpus import Analysis
+
+from sklearn.neural_network import MLPClassifier, MLPRegressor
+from sklearn import preprocessing
+from sklearn.model_selection import train_test_split
+import itertools
+#from sklearn.model_selection import train_test_split
+from sklearn.preprocessing import StandardScaler
+from sklearn.linear_model import SGDRegressor
+from sklearn.metrics import mean_squared_error, r2_score
+from sklearn import preprocessing
+from sklearn import linear_model
+from sklearn.metrics import confusion_matrix
+import pylab as pl
+
+
+from sklearn import preprocessing
+#from sklearn.model_selection import train_test_split
+#from sklearn.preprocessing import StandardScaler
+#from sklearn.linear_model import SGDRegressor
+from sklearn.linear_model import SGDClassifier
+from sklearn.metrics import mean_squared_error, r2_score
+from sklearn import preprocessing
+import sklearn
+
+#from neuronunit.optimisation.optimisation_management import stochastic_gradient_descent
+import seaborn as sns
 
 #import seaborn as sns; sns.set()  # for plot styling
 
@@ -61,14 +87,20 @@ def proc_xml(FILES):
         urlDats.append(urlDat)
     return urlDats
 
+#import online_app_backend
+#files = online_app_backend.download_course()
+#import pdb; pdb.set_trace()
 try:
     with open('traingDats.p','rb') as f:
         trainingDats = pickle.load(f)
+
 except:
 
     trainingDats = proc_xml(FILES)
     with open('traingDats.p','wb') as f:
         pickle.dump(trainingDats,f)
+
+
 
 FILES = natsorted(glob.glob(str(os.getcwd())+'/results_dir/*.p'))
 A = Analysis(FILES, min_word_length = 200)
@@ -80,6 +112,31 @@ not_science = [ t for t in not_science if 'standard' in t.keys() ]
[…]

### 2019-10-17 Examples/wiki_only.py

@@ -2,11 +2,7 @@
 import os
 
 from os import path
-try:
-    from wordcloud import WordCloud
-except:
-    print('simply pip install wordcloud from inside this dockerbuild')
-    
+from wordcloud import WordCloud
 import matplotlib
 matplotlib.use('Agg')
 import pdb
@@ -31,6 +27,17 @@ from SComplexity import get_bmark_corpus as gbc
 
 import pickle
 texts = pickle.load(open('pickles/scraped_new.p','rb'))
+mean_wiki_pedia = []
+for t in texts:
+    if t['wiki'] == True:
+        if str('standard') in t.keys():
+
+            mean_wiki_pedia.append(t['standard'])
+mwp = np.mean(mean_wiki_pedia)
+print(mwp)
+import pdb
+pdb.set_trace()
+
 ARTCORPUS = pickle.load(open('traingDats.p','rb'))
 acorpus = ''
 for t in ARTCORPUS:
@@ -40,7 +47,6 @@ for t in ARTCORPUS:
             acorpus+=str(' ')+s
 import matplotlib.pyplot as plt
 
-#import pdb; pdb.set_trace()
 
 def art_cloud(acorpus):
 
@@ -49,7 +55,7 @@ def art_cloud(acorpus):
     plt.imshow(wordcloud, interpolation='bilinear')
     plt.axis("off")
     plt.savefig('acorpus.png')# Generate a word cloud image
-art_cloud(acorpus)
+#art_cloud(acorpus)
 try:
     references = pickle.load(open('../SComplexity/benchmark_bu.p','rb'))
     print(references[-1]['standard'])
@@ -76,16 +82,6 @@ for t in texts:
         for s in t['tokens']:
             wikis+=str(' ')+s
 
-mean_wiki_pedia = []
-for t in texts:
-    if t['wiki'] == True:
-        if str('standard') in t.keys():
-
-            mean_wiki_pedia.append(t['standard'])
-mwp = np.mean(mean_wiki_pedia)
-print(mwp)
-import pdb
-pdb.set_trace()
 
 def make_word_clouds(pre_science,pre_not_science,wikis):
     with open('science.csv', 'w') as f:

### 2019-10-17 SComplexity/crawl.py

@@ -44,17 +44,19 @@ from pdfminer.layout import LAParams
 from pdfminer.converter import  TextConverter
 
 import re
+import numpy as np
+
 
 from bs4 import BeautifulSoup
 import bs4 as bs
 import urllib.request
 
-from io import StringIO
-import io
-
 from delver import Crawler
 C = Crawler()
 CWD = os.getcwd()
+
+from io import StringIO
+import io
 
 
 rsrcmgr = PDFResourceManager()
@@ -107,6 +109,33 @@ def denver_to_text(url):
     file.close()
     return text
 
+def collect_hosted_files(url):
+    '''
+    Used for scholar
+    '''
+    print(url)
+    try:
+        crude_html = denver_to_text(url)
+    except:
+        driver.get(url)
+        crude_html = driver.page_source
+    #soup0 = BeautifulSoup(crude_html, 'html.parser')
+    soup = BeautifulSoup(crude_html, 'lxml')
+    links = []
+    print(soup)
+    for link in soup.findAll('a'):check_out = link.get('href');links.append(check_out)
+        #print(link)
+    for link in soup.findAll('a', attrs={'href': re.compile("https://")}):
+        check_out = link.get('href')
+        #if '/citations?' in check_out:
+        links.append(check_out)
+    for link in soup.findAll('a', attrs={'href': re.compile("http://")}):
+        check_out = link.get('href')
+        #if '/citations?' in check_out:
+        links.append(check_out)
+    #import pdb; pdb.set_trace()
+
+    return links
 
 def collect_pubs(url):
     '''
@@ -124,4 +153,9 @@ def collect_pubs(url):
         check_out = link.get('href')
         #if '/citations?' in check_out:
         links.append(check_out)
+    for link in soup.findAll('a', attrs={'href': re.compile("http://")}):
+        check_out = link.get('href')
+        #if '/citations?' in check_out:
+        links.append(check_out)
+
     return links

### 2019-10-17 SComplexity/get_bmark_corpus.py

@@ -7,22 +7,23 @@ import numpy as np
 import requests
 from bs4 import BeautifulSoup
 
-from delver import Crawler
 from SComplexity.crawl import collect_pubs, convert_pdf_to_txt#,process
 from SComplexity.scrape import convert
 from SComplexity.t_analysis import text_proc
 from SComplexity.utils import black_string
 
+from delver import Crawler
 C = Crawler()
 
 def process(link):
     urlDat = {}
     urlDat['link'] = link
     urlDat['page_rank'] = 'benchmark'
+
     try:
         if str('pdf') not in link:
             content = C.open(link).content
-            
+
             soup = BeautifulSoup(content, 'html.parser')
             for script in soup(["script", "style"]):
                 script.extract()    # rip it out
@@ -32,16 +33,17 @@ def process(link):
             lines = (line.strip() for line in text.splitlines())  # break into lines and remove leading and trailing space on each
             chunks = (phrase.strip() for line in lines for phrase in line.split("  ")) # break multi-headlines into a line each
             text = '\n'.join(chunk for chunk in chunks if chunk) # drop blank lines
-            buffer = str(text)
+            bufferd = str(text)
         else:
             pdf_file = requests.get(link, stream=True)
-            buffer = convert_pdf_to_txt(pdf_file)
+            bufferd = convert_pdf_to_txt(pdf_file)
 
-        urlDat = text_proc(buffer,urlDat)
+        urlDat = text_proc(bufferd,urlDat)
+
     except:
         print('bummer dude')
         #content = C.open(link).content
-        #print(content)    
+        #print(content)
         urlDat = None
     return urlDat
 
@@ -51,12 +53,36 @@ def process(link):
 #        urlDats = pickle.load(f)
 #except:
 
-def mess_length(word_length):
+def mess_length(word_length,bcm):
     with open('bcm.p','rb') as f:
-        pickle.load(big_complex_mess,f)
+        big_complex_mess = pickle.load(big_complex_mess,f)
     reduced = big_complex_mess[0:word_length]
-    pmegmess = text_proc(reduced)
-    return mess_length
+    urlDat = {}
+    pmegmess = text_proc(reduced,urlDat)
+    return mess_length, pmegmess
+
+def get_greg_nicholas():
[…]

### 2019-10-17 SComplexity/pat_versus_ben.py

@@ -1,0 +1,3 @@
+import pickle
+patrick = pickle.load('patrick.p','rb')
+ben_results = pickle.load('ben_results.p','rb')

### 2019-10-17 SComplexity/plotting_author_versus_distribution.py

@@ -16,7 +16,8 @@ def find_nearest(array, value):
 bmark = pickle.load(open('benchmarks.p','rb'))
 NAME,ar = pickle.load(open('more_authors_results.p','rb'))
 #print(ar)
-#import pdb; pdb.set_trace()
+print(bmark)
+import pdb; pdb.set_trace()
 import os
 
 if os.path.exists('traingDats.p'):
@@ -93,7 +94,7 @@ def get_heights(stats_items,histogram_content,x_sub_set):
     return heights, bin_width_offset
 
 bmark_stats_items = [ b['standard'] for b in bmark ]
-categories = [ "upgoer 5", "Readibility Declining Over Time","Science of Writing","Post Modern Essay Generator"]
+categories = [ "upgoer 5", "Readibility Declining Over Time","Science of Writing","Post Modern Essay Generator","G Nicholas"]
 #categories = [b['link'] for b in bmark]
 bmark_heights, bwo = get_heights(bmark_stats_items,histogram_content,x_sub_set)
 heights, bwo = get_heights(stats_items,histogram_content,x_sub_set)

### 2019-10-17 setup.py

@@ -1,8 +1,8 @@
 
 #!/usr/bin/env python
 # old functional:
-from distutils.core import setup
-import setuptools
+#from distutils.core import setup
+#import setuptools
 
 # new dysfunctional.
 try:
@@ -10,14 +10,13 @@ try:
 except ImportError:
     from distutils.core import setup, find_packages
 
-from setuptools import setup#, find_packages
 
 def read_requirements():
     '''parses requirements from requirements.txt'''
     reqs_path = os.path.join('.', 'requirements.txt')
     install_reqs = parse_requirements(reqs_path, session=PipSession())
     reqs = [str(ir.req) for ir in install_reqs]
-return reqs
+    return reqs
 
 
 setup(name='scomplexity',

### 2019-10-17 Publication/tex_manuscript/manuscript.tex
JOSS figure and notebook added

@@
 
-\subsection{}keywords} 
+\section{The issue of Irreducible Complexity}
+It has been observed that the readability of scientific texts is declining with increased time[].
+Decreasing readability, is usually due to increased writting complexity.
+One could argue that scientific writing is increasing in complexity, as this reflects, the obvious advances in science methods and analysis, which increase the complexity in the act of simply doing science.
+Afterall manys cientific advances add details to existing complex models and imaging techniques.\\
+\\
+Given that the act of science is becoming more complex, is it reasonable to argue that all scientific writing needs to be complex in order to capture irreducible complexity?
+We argue that there are some great counter examples to the idea of irreducible complexity.\\
+\\
+
+\subsubsection{}keywords} 
 Bag of words analysis, naive Bayes.
@@
 \section{Introduction}
-# Science Accessibility Project
-## Motivation for the Science Accessibility Project
 Non-scientific writing typically exceeds genuine scientific writing in one important criteria: in contrast to genuine science non-science ideas are often expressed with a more accessible writing style.
@@
 \\
-Objectively describing the different character of the different writing styles will allow us to prescribe how, to shift academic science writing into a more accessible niche, where science can more aggressively compete with pseudo-science, and blogs, facilitating greater knowledge transference, at a moment in history when public awareness is critically at stake.
-
-## Machine Estimation of Writing Complexity.
+Objectively describing the different character of the different writing styles will allow us to prescribe how, to shift academic science writing into a more accessible niche, where science can more aggressively compete with pseudo-science, and blogs, facilitating greater knowledge transference, at a moment in history when public awareness is critically at stake.\\
+\\
 The accessibility of written word can be approximated by a computer program that reads over the text, and guesses the mental difficulty, associated with comprehending a written document.

### 2019-10-17 Examples/ml.jl

@@ -12,9 +12,6 @@ function trypy()
 
         Pkg.test("PyCall")
         plt = pyimport("matplotlib.pyplot")
-        x = range(0;stop=2*pi,length=1000); y = sin.(3*x + 4*cos.(2*x));
-        plt.plot(x, y, color="red", linewidth=2.0, linestyle="--")
-        plt.show()
 
 		#return unreliable_connect()
 	catch ex
@@ -22,10 +19,8 @@ function trypy()
         Pkg.test("PyCall")
         math = pyimport("math")
         math.sin(math.pi / 4) # returns ≈ 1/√2 = 0.70710678...
-	   end
+   end
 end
-#trypy()
-#try
 try
 	using Knet
 	using PyCall
@@ -43,23 +38,53 @@ catch
 	#Pkg.rm("StatPlots")
 	Pkg.add("StatsPlots")
 	#Pkg.add("Gallium")
-	Pkg.add(“GR”)
-    Pkg.add("IJulia");
-    Pkg.add("Plots");
-    Pkg.add("StatsPlots"); #to install the StatPlots package.
-    Pkg.add("DataFrames");
+	Pkg.add("GR")
+    Pkg.add("IJulia")
+    Pkg.add("Plots")
+    Pkg.add("StatsPlots") #to install the StatPlots package.
+    Pkg.add("DataFrames")
 	Pkg.add("Seaborn")
 	Pkg.add("PyPlot")
+
     using DataFrames
     using IJulia
-	#using Gallium
 	using Knet
-
     using Plots;
     using StatsPlots;
     using PyCall
 end
 
+@pyimport pickle
+f = pybuiltin("open")("scraped_new.p","rb")
+p = pickle.Unpickler(f)
+scraped_new = p[:load]()
+f[:close]()
+scraped_new[1]["wcount"]
+wc = [ sn["wcount"] for sn in scraped_new ]
+sp = [ sn["sp"] for sn in scraped_new ]
+#subjectivity = [ sn["ss"] for sn in scraped_new ]
+features = {}
+features = Dict()
+subjectivity = [ sn["ss"] for sn in scraped_new if haskey(sn,"ss") ]
+features["ss"] = subjectivity
+features["ss"] = wc
+features["sp"] = sp
+
+#var	info(sn)
+gr()
+histogram(sn)
+#using PyPlot
+#h = PyPlot.plt.hist(sn)
[…]
